\texttt{MSnbase}, efficient R-based access and manipulation of raw mass spectrometry data

### 2019-05-31 msnbase2.Rnw
use Rnw file and Makefile
start intro

@@

\item{potential for reuse}: see \cite{Wieczorek:2017,Griss:2019,Smith:2006}.
\item{general limitations}
\item{system limitations}
\item{end-user documentation}
\item{developer documentation}
\item{sample data}
\item{benchmark data set}
\item{availability}
\item{license information}
\item{system requirements}

@@

>>>>

Mass spectrometry is a powerful technology to assays chemical and
biological samples. It is used routinely, with well characterised
protocol, as well a development platform, to improve on existing
methods and devise new ones to analyse ever more complex sample in
greater details. The complexity and diversity of mass spectrometry
yields data that is itself complex and often times of considerable
size, that requires non trivial processing before producing
interpretable results. This is particularly relevant, and can
constitue a significant challenge for method developers that, in
addition to the development of sample processing and mass spectrometry
methods, need to process and analyse these new data to demonstrate the
improvement in their technical and analytical work.

There exists a very diverse catalogue of software tools to explore,
process and interpret mass spectrometry data. These range from low
level software libraries such as vendor libraries, jmzML (ref),
proteowizard (ref), ... that are aimed at programmers to develop new
applications, to user-oriented applications,  such as ProteomeDiscoverer, MaxQuant, ...

The former are used through application programming interfaces
exclusively, while the latter generally featuring graphical user
interfaces (GUI).

Give examples of libraries re-used in user/gui focused application

In this software note, we are going to focus on metabolomics and
proteomics applications of mass spectrometry.

@@

\item{potential for reuse}: see
  \cite{Wieczorek:2017,Griss:2019,Smith:2006} for examples.
\item{general limitations}
\item{system limitations}
\item{end-user documentation}
\item{developer documentation}
\item{sample data}
\item{benchmark data set}
\item{availability}
\item{license information}
\item{system requirements}

@@

The version of \texttt{MSnbase} used in this manuscritp is version
\Sexpr{packageVersion("MSnbase")}. The main features presented here
were available since version 2.0.
